Placeholder

### 2021-02-09 Paper_Histograms.Rmd
Plotted age, gender and employment retro together with additional data labels for gender

>>>>

```{r Plot age gender employ and ethnicity retro together}

dat.retro_gender_distribution <- dat.retro %>% 
  group_by(Gender_collapsed, Sample_plot) %>% 
  summarise(n = n())

labelled_arranged_gender_plot <- dat.retro_gender_distribution %>% 
  ggplot(aes(x = Gender_collapsed, y = n, fill = Sample_plot)) +
  geom_bar(position = "dodge", stat = "identity") +
  scale_fill_manual(values = COPINGpalette3) +
  theme_classic() +
  theme(plot.title = element_text(hjust = 0.5),
        plot.subtitle = element_text(hjust = 0.5)) +
  labs(x = "Participant Gender",
       y = "N participants") +
  theme(legend.position = "none") + 
  theme(legend.title = element_blank()) +
  geom_text(aes(label = n),
            size = 3,
            position = position_dodge(width=0.9), 
            vjust=-0.25) +
  scale_x_discrete(guide = guide_axis(n.dodge = 2),
                   expand = expansion(mult = c(0.3, 0.4))) +
  scale_y_continuous(expand = expansion(mult = c(0, 0.1)))

#Combine retro age, gender and employ together
ggarrange(retro_age_plot, 
          ggarrange(labelled_arranged_gender_plot, arranged_employ_plot, ncol = 2), 
          nrow = 2,
          common.legend = TRUE)
